Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-12-05 2016-Weak-FH-Bisim/WeakBisim.tex
updated the listing in last appendix

state a0
transition in(msg) -> a1 {a1_msg:=msg}

state a1
vars a1_msg:Data {m1_c:=0}:Int

transition out(a1_msg, m1_c) -> a0
transition synchro($tau)  -> a1 {m1_c:=m1_c+1}

pNet SimpleProtSpec2
holes P,Q
subnets P,M1,Q
vars p_a,q_a:Action m:Data c:Int

vector SV0 <p_send(m), in(m),_>->p_send(m)
vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
vector SV2 <_, out(m,c), q_recv(m)>->q_recv(m,c)
vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m)]

@@

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
SimpleProtImpl:
import "Data_Alg.algp"

root SimpleProtImpl2

const in,out:Action
const tau,p_send,q_recv,m_recv,m_send,m_error: Action
const s_send,s_ack,s_error,r_recv,r_ack: Action

@@

state s0
transition in(msg) -> s1 {s1_msg:=msg, s1_c:=0}

state s1
vars s1_msg:Data s1_c:Int
transition s_send(s1_msg, s1_c) -> s2

@@

state r1
vars r1_msg:Data r1_c:Int
transition out(r1_msg, r1_c) -> r2

@@

pNet medium
subnets Sender, M1, Receiver
vars m:Data c:Int
vector SV0 <in(m), _, _>->in(m)
vector SV1 <s_send(m,c), m_recv(m,c), _>->synchro($tau)
vector SV2 <_, m_send(m), r_recv(m)>->synchro($tau)
vector SV3 <$s_ack, _, $r_ack>->synchro($tau)
vector SV4 <$s_error, $m_error, _>->synchro($tau)
vector SV5 <_, _, out(m,c)>->out(m,c)

pNet SimpleProtImpl2
holes P,Q
subnets P,medium,Q
vars p_a,q_a:Action  m:Data c:Int
vector SV0 <p_send(m), in(m),_>->in(m)
vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
vector SV2 <_, out(m,c), q_recv(m,c)>->out(m,c)
vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m,c)]
\end{lstlisting}

@@

Finaly, we list here, in raw format, the 12 OTs computed by the tool
\TODO{BUG! We should have 19 OTs...}:

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
INFO  SimpleProtImpl2 - 
	{P|->p_send(m:sva_SV6:1:1)},
	[(msg=m:sva_SV6:1:1)/\((in(msg))=(in(m:sva_SV6:1:1)))],
	{s1_msg := msg, s1_c := 0}
OT:1 ------------------------------------------------------------
	<s0_a0_r0>-----in(m:sva_SV6:1:1)----><s1_a0_r0>

@@

INFO  SimpleProtImpl2 - 
	{},   [(s1_msg=m:sva_SV1:114:2)/\(s1_c=c:sva_SV1:114:2)
	  /\((s_send(s1_msg, s1_c))=(s_send(m:sva_SV1:114:2, c:sva_SV1:114:2)))
          /\(msg=m:sva_SV1:114:2)/\(c=c:sva_SV1:114:2)
          /\((m_recv(msg, c))=(m_recv(m:sva_SV1:114:2, c:sva_SV1:114:2)))],
	{a1_msg := msg, a1_c := c}
OT:6 ------------------------------------------------------------
	<s1_a0_r0>-----_tau_----><s2_a1_r0>

@@

INFO  SimpleProtImpl2 - 
	{},   [],   {}
OT:9 ------------------------
	<s2_a1_r0>-----_tau_----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
	{P|->p_a:sva_SV7:1:2},
	[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
OT:10 ------------------------------------------------------------
	<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
	{Q|->q_a:sva_SV9:1:4},
	[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4.
          (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
OT:11 ------------------------------------------------------------
	<s2_a2_r0>-----q_a:sva_SV9:1:4----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
	{},   [],   {s1_c := s2_c+1}
OT:12 --------------------------------------
	<s2_a2_r0>-----_tau_----><s1_a0_r0>

INFO   SimpleProtImpl2 - State variables:

Global State: <s0_a0_r0>
===================
pLTS States: <s0 vars: {}> <a0 vars: {}> <r0 vars: {}>

Global State: <s1_a0_r0>
===================
pLTS States: <s1 vars: { s1_c <-{0, s2_c+1, } s1_msg <-{msg, }}> <a0 vars: {}> <r0 vars: {}>

Global State: <s2_a1_r0>
===================
pLTS States: <s2 vars: {}> <a1 vars: { a1_msg <-{msg, } a1_c <-{c, }}> <r0 vars: {}>

Global State: <s2_a2_r0>
===================
pLTS States: <s2 vars: {}> <a2 vars: {}> <r0 vars: {}>

INFO  SimpleProtImpl2 - Total: 12 SATISFIABLE OTs
INFO  SimpleProtImpl2 -        122 UNSATISFIABLE OTs
INFO  SimpleProtImpl2 - Total Time: 657 ms

>>>>

state a0
transition in(msg) -> a1 {a1_msg:=msg, m1_ec:=0}

state a1
vars a1_msg:Data m1_ec:Int
transition out(a1_msg, m1_ec) -> a0
transition synchro($tau)  -> a1 {m1_ec:=m1_ec+1}

pNet SimpleProtSpec2
holes P,Q
subnets P,M1,Q
vars p_a,q_a:Action m:Data ec:Int

vector SV0 <p_send(m), in(m),_>->synchro(in(m))
vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
vector SV2 <_, out(m,ec), q_recv(m)>->synchro(out(m,ec))
vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m)]

@@

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
SimpleProtImpl2:
import "Data_Alg.algp"
root SimpleProtImpl2

const in,out:Action
const tau,p_send,q_recv,m_recv,m_send,m_error: Action
const s_recv,s_send,s_ack,s_error,r_recv,r_ack,r_send: Action

@@

state s0
transition s_recv(msg) -> s1 {s1_msg:=msg, s1_c:=0}

state s1
vars s1_msg:Data s1_c:Int
transition s_send(s1_msg, s1_c) -> s2 {s2_c:=s1_c}

@@

state r1
vars r1_msg:Data r1_c:Int
transition r_send(r1_msg, r1_c) -> r2

@@

pNet medium
  subnets Sender, M1, Receiver
  vars m:Data c:Int
vector SV0 <s_recv(m), _, _>->in(m)
vector SV1 <s_send(m,c), m_recv(m,c), _>->synchro($tau)
vector SV2 <_, m_send(m,c), r_recv(m,c)>->synchro($tau)
vector SV3 <$s_ack, _, $r_ack>->synchro($tau)
vector SV4 <$s_error, $m_error, _>->synchro($tau)
vector SV5 <_, _, r_send(m,c)>->out(m,c)

pNet SimpleProtImpl2
  holes P,Q
  subnets P,medium,Q
  vars p_a,q_a:Action  m:Data c:Int
vector SV0 <p_send(m), in(m),_>->synchro(in(m))
vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
vector SV2 <_, out(m,c), q_recv(m,c)>->synchro(out(m,c))
vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m,c)]
\end{lstlisting}

@@

Finaly, we list here, in raw format, the 19 OTs computed by the tool for the SimpleProtImpl pNet:

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
INFO  SimpleProtImpl2 - 
{P|->p_send(m:sva_SV6:1:1)},
[(msg=m:sva_SV0:12:1)/\((s_recv(msg))=(s_recv(m:sva_SV0:12:1)))],   {s1_msg := msg, s1_c := 0}
	OT:1 ------------------------------------------------------------
		<s0_a0_r0>-----_in(m:sva_SV6:1:1)_----><s1_a0_r0>

@@

INFO  SimpleProtImpl2 - 
{},   [(s1_msg=m:sva_SV1:114:2)/\(s1_c=c:sva_SV1:114:2)
  /\((s_send(s1_msg, s1_c))=(s_send(m:sva_SV1:114:2, c:sva_SV1:114:2)))
  /\(msg=m:sva_SV1:114:2)/\(c=c:sva_SV1:114:2)
  /\((m_recv(msg, c))=(m_recv(m:sva_SV1:114:2, c:sva_SV1:114:2)))],
{s2_c := s1_c, a1_msg := msg, a1_c := c}
	OT:6 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

@@

INFO  SimpleProtImpl2 - 
{},   [(a1_msg=m:sva_SV2:114:3)/\(a1_c=c:sva_SV2:114:3)
  /\((m_send(a1_msg, a1_c))=(m_send(m:sva_SV2:114:3, c:sva_SV2:114:3)))
  /\(msg=m:sva_SV2:114:3)/\(c=c:sva_SV2:114:3)
  /\((r_recv(msg, c))=(r_recv(m:sva_SV2:114:3, c:sva_SV2:114:3)))],
{r1_msg := msg, r1_c := c}
	OT:9 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a0_r1>

INFO  SimpleProtImpl2 - 
		{},   [],   {}
	OT:10 ------------------------
		<s2_a1_r0>-----_tau_----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
{P|->p_a:sva_SV7:1:2},
[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:11 ------------------------------------------------------------
		<s2_a0_r1>-----p_a:sva_SV7:1:2----><s2_a0_r1>

INFO  SimpleProtImpl2 - 
{Q|->q_recv(m:sva_SV8:1:3, c:sva_SV8:1:3)},
[(r1_msg=m:sva_SV5:18:6)/\(r1_c=c:sva_SV5:18:6)
  /\((r_send(r1_msg, r1_c))=(r_send(m:sva_SV5:18:6, c:sva_SV5:18:6)))],   {}
	OT:12 ------------------------------------------------------------
		<s2_a0_r1>-----_out(m:sva_SV8:1:3, c:sva_SV8:1:3)_----><s2_a0_r2>

INFO  SimpleProtImpl2 - 
{Q|->q_a:sva_SV9:1:4},
[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:13 ------------------------------------------------------------
		<s2_a0_r1>-----q_a:sva_SV9:1:4----><s2_a0_r1>

INFO  SimpleProtImpl2 - 
{P|->p_a:sva_SV7:1:2},
[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:14 ------------------------------------------------------------
		<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
{Q|->q_a:sva_SV9:1:4},
[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:15 ------------------------------------------------------------
		<s2_a2_r0>-----q_a:sva_SV9:1:4----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
		{},   [],   {s1_c := s2_c+1}
	OT:16 --------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
{P|->p_a:sva_SV7:1:2},
[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:17 ------------------------------------------------------------
		<s2_a0_r2>-----p_a:sva_SV7:1:2----><s2_a0_r2>

INFO  SimpleProtImpl2 - 
{Q|->q_a:sva_SV9:1:4},
[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:18 ------------------------------------------------------------
		<s2_a0_r2>-----q_a:sva_SV9:1:4----><s2_a0_r2>

INFO  SimpleProtImpl2 - 
		{},   [],   {}
	OT:19 ------------------------
		<s2_a0_r2>-----_tau_----><s0_a0_r0>

DEBUG SimpleProtImpl2 - 
Global State: <s0_a0_r0>
===================
pLTS States: <s0 vars: {}> <a0 vars: {}> <r0 vars: {}>

DEBUG SimpleProtImpl2 - 
Global State: <s1_a0_r0>
===================
pLTS States: <s1 vars: { s1_msg <-{msg, } s1_c <-{0, s2_c+1, }}> <a0 vars: {}> <r0 vars: {}>

DEBUG SimpleProtImpl2 - 
Global State: <s2_a1_r0>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a1 vars: { a1_msg <-{msg, } a1_c <-{c, }}> <r0 vars: {}>

DEBUG SimpleProtImpl2 - 
Global State: <s2_a0_r1>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a0 vars: {}> <r1 vars: { r1_c <-{c, } r1_msg <-{msg, }}>

DEBUG SimpleProtImpl2 - 
Global State: <s2_a2_r0>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a2 vars: {}> <r0 vars: {}>

DEBUG SimpleProtImpl2 - 
Global State: <s2_a0_r2>
===================
pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a0 vars: {}> <r2 vars: {}>

INFO  SimpleProtImpl2 - Total: 19 SATISFIABLE OTs
INFO  SimpleProtImpl2 -        185 UNSATISFIABLE OTs
INFO  SimpleProtImpl2 - Total Time: 1105 ms
